### 2021-04-22 Chapter-5/Chapter-5.tex
Updates from Overleaf

We consider an attacker who shares the same hardware resource with the victim. The attacker may not know the memory access the victim program accesses directly, but he can infer whether some memory addresses are accessed or not at various granularities after \textit{each run} of the victim program. We call the memory access information as the observation ($O$) in the rest of the paper. This is a typical scenario for most side-channel attacks.  We also assume the attacker can have access to the source code of the victim program ($\beta$). It is a valid assumption since most side-channel attacks target open source software. Also like recent works, we assume the attacker have a noise-free observation. For some side-channel channels like the controlled-channel attacks, it is already true. The program ($\beta$) has $K$ as the sensitive input. $K$ is a finite set that consists of every possible keys ($k \in K$). The program also takes known messages $M$ as the input.

>>>>

We consider an attacker who shares the same hardware resource with the victim. The attacker may not know the memory access the victim program accesses directly. Still, he can infer whether some memory addresses are accessed or not at various granularities after \textit{each run} of the victim program. We call the memory access information as the observation ($O$) in the rest of the paper. This is a typical scenario for most side-channel attacks.  We also assume the attacker can have access to the source code of the victim program ($\beta$). It is a valid assumption since most side-channel attacks target open-source software. Also, like recent works, we assume the attacker has a noise-free observation. For some side-channel channels like the controlled-channel attacks, it is already true. The program ($\beta$) has $K$ as the sensitive input. $K$ is a finite set that consists of every possible key ($k \in K$). The program also takes known messages $M$ as the input.
